Positivity-Preserving Adaptive Runge--Kutta Methods

### 2020-05-04 nusslein_vsrp/latex/overview.tex

Our proposed method is summarized in Algorithm\,\ref{alg:Adaption}.

@@

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\While{$t<t_{end}$}
\State Choose $\Delta t$
\State Calculate $F = (f_1, \dots, f_s)$ \eqref{eq:stagevalues}
\State Set $u^{n+1}=u^n + \Delta t Fb$ \eqref{eq:Combination}
\If {$u^{n+1} \geq 0$}
	\State $success = True$
\Else
	\State{$\tilde p = p_{start}$}
	\While{$\tilde p \geq p_{min}$}
		\State Solve LP \eqref{eq:free-adaptation}
		\If {LP Feasible \textbf{and} result correct}
			\State $\delta = \| \Delta t F(\bt-b)\|$
			\If {$\delta < tol$}
				\State $u^{n+1}=u^n+\Delta t F \tilde b$
				\State $success = True$
				\State \textbf{break}
			\EndIf
		\EndIf
		\If {$\tilde p = p_{min}$}
			\State $sucess=False$
		\EndIf
		\State $\tilde p = \tilde p -1$
	\EndWhile
\EndIf
\If {$sucess$}
% 	\State $u^n=u^{n+1},t^n=t^{n+1}+\Delta t,n=n+1$
	\State Set $n=n+1$ and continue
\EndIf
\EndWhile
\end{algorithmic}
\caption{Pseudocode for the algorithm using a free adaption of weights.}
\label{alg:Adaption}
\end{algorithm}

>>>>

Our proposed method to solve a positive initial value problem \eqref{ode}
is summarized in Algorithm\,\ref{alg:Adaption}.

@@

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\State Initialize $n \leftarrow 0$, $u^n \leftarrow u_0$, $t \leftarrow 0$
\While{$t<t_{end}$}
\State Choose $\Delta t$ (fixed or via an adaptive stepsize control)
\State Calculate $F = (f_1, \dots, f_s)$, cf.\ \eqref{eq:stagevalues}
\State $u^{n+1} \leftarrow u^n + \Delta t Fb$, cf.\ \eqref{eq:Combination}
\If {$u^{n+1} \geq 0$}
	\State $success \leftarrow True$
\Else
	\State{$\pt \leftarrow p_{start}$}
	\While{$\pt \geq p_{min}$}
		\State Solve LP \eqref{eq:free-adaptation}
		\If {LP is feasible \textbf{and} result is correct} \todo{TODO: define these}
			\State $\delta \leftarrow \| \Delta t F(\bt-b)\|$
			\If {$\delta < tol$}
				\State $u^{n+1} \leftarrow u^n+\Delta t F \tilde b$
				\State $success \leftarrow True$
				\State \textbf{break}
			\EndIf
		\EndIf
		\If {$\pt = p_{min}$}
			\State $sucess \leftarrow False$
		\EndIf
		\State $\pt \leftarrow \pt - 1$
	\EndWhile
\EndIf
\If {$sucess$}
	\State $t \leftarrow t + \dt$, $n \leftarrow n+1$ and continue
\Else
  \State \todo{TODO}
\EndIf
\EndWhile
\end{algorithmic}
\caption{Pseudocode for the algorithm using a free adaption of weights.}
\label{alg:Adaption}
\end{algorithm}
